---
title: "linearmodel"
author: "Jordan Rose"
date: "11/21/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
dataF <- read.csv(file="http://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(knitr)
```

## Now with ggplot - first select the basic data

```{r}
basicA <- ggplot(dataF,aes(y=SIMS,x=ARM))
```

## Now add in scatterplot

```{r}
basicA + geom_point()+ geom_smooth(method=lm)
``` 

# Inferential  (Build linear model)
  
```{r}
model.A <- lm(SIMS~ARM,data=dataF)
summary.lm(model.A)
pdata=data.frame(GRIP=94,ARM=88)
predict(model.A,pdata,interval="prediction")
```

We made the model and the prediction interval went from -1.72 to a positive 3.13.

## Now with ggplot - first select the basic data

```{r}
basicG <- ggplot(dataF,aes(y=SIMS,x=GRIP))
```

## Now add in scatterplot

```{r}
basicG + geom_point()+ geom_smooth(method=lm)
``` 

# Inferential  (Build linear model)
  
```{r}
model.1 <- lm(SIMS~GRIP,data=dataF)
summary.lm(model.1)
```

# Inferential  (Build linear model)
  
```{r}
model.G <- lm(SIMS~GRIP,data=dataF)
summary.lm(model.G)
pdata=data.frame(GRIP=94,ARM=88)
predict(model.G,pdata,interval="prediction")
```

The prediction model went from a -3.10 to a postive 2.03

# Inferential  (Build linear model)
  
```{r}
model.1 <- lm(SIMS~GRIP+ARM,data=dataF)
summary.lm(model.1)
```

# Inferential  (Build linear model)
  
```{r}
model.G <- lm(SIMS~GRIP,data=dataF)
summary.lm(model.G)
```